Equalizer 2.0\\Convergence of a Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
Resolve references
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@29 db7c848b-7755-4df2-b763-8796797afa52

To benchmark the data distribution we used two datasets: The david statue at 2mm
resolution (\fig{fDavid2mm}) and 3D volumes of a spike frequencies of a 3
million neuron simulation (\fig{fVolumes}).

\begin{figure}[ht]\center
  \includegraphics[width=.49\columnwidth]{images/spikes512}\hfil
  \includegraphics[width=.49\columnwidth]{images/spikes1280}
  \caption{\label{fVolumes}Spike frequencies of a 3 million neuron simulation at
    437x240x512 (51MB, left) and 1092x600x1280 (800MB, right) resolution}
\end{figure}

>>>>

To benchmark the data distribution we used two datasets: The david statue at 2mm
resolution (\fig{fDavid2mm}) and 3D volumes of a spike frequencies of an
electrical simulation of three million neurons (\fig{fVolumes}).

\begin{figure}[ht]\center
  \includegraphics[width=.49\columnwidth]{images/spikes512}\hfil
  \includegraphics[width=.49\columnwidth]{images/spikes1280}
  \caption{\label{fVolumes}Spike frequencies of a three million neuron
    electrical simulation at 437x240x512 (51MB, left) and 1092x600x1280 (800MB,
    right) resolution}
\end{figure}
